### 2024-10-16 time-series-analysis.qmd
20241016 - add alt-text to figures

```{r}
#| label: fig-timeSeriesHistoricalTomBrady
#| fig-cap: "Tom Brady's Historical Fantasy Points by Game."

@@

```{r}
#| label: fig-timeSeriesHistoricalBradyManning
#| fig-cap: "Historical Fantasy Points by Game for Tom Brady and Peyone Manning."

@@

```{r}
#| label: fig-timeSeriesACFtomBrady
#| fig-cap: "Autocorrelation Function (ACF) Plot of Tom Brady's Historical Fantasy Points by Game."

@@

```{r}
#| label: fig-arimaTomBrady
#| fig-cap: "Model Summary of Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."

@@

```{r}
#| label: fig-arimaModifiedTomBrady
#| fig-cap: "Model Summary of modified Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."

@@

```{r}
#| label: fig-arimaPeytonManning
#| fig-cap: "Model Summary of Autoregressive Integrated Moving Average Model fit to Peyton Manning's Historical Performance by Game."

@@

```{r}
#| label: fig-timeSeriesProjectionTomBrady
#| fig-cap: "Tom Brady's Historical and Projected Fantasy Points by Game."

@@

```{r}
#| label: fig-timeSeriesProjectionPeytonManning
#| fig-cap: "Peyton Manning's Historical and Projected Fantasy Points by Game."

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeQB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Quarterbacks."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeRB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Running Backs."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeWR
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Wide Receivers."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeTE
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Tight Ends."
#| code-fold: true

>>>>

```{r}
#| label: fig-timeSeriesHistoricalTomBrady
#| fig-cap: "Tom Brady's Historical Fantasy Points by Game."
#| fig-alt: "Tom Brady's Historical Fantasy Points by Game."

@@

```{r}
#| label: fig-timeSeriesHistoricalBradyManning
#| fig-cap: "Historical Fantasy Points by Game for Tom Brady and Peyone Manning."
#| fig-alt: "Historical Fantasy Points by Game for Tom Brady and Peyone Manning."

@@

```{r}
#| label: fig-timeSeriesACFtomBrady
#| fig-cap: "Autocorrelation Function (ACF) Plot of Tom Brady's Historical Fantasy Points by Game."
#| fig-alt: "Autocorrelation Function (ACF) Plot of Tom Brady's Historical Fantasy Points by Game."

@@

```{r}
#| label: fig-arimaTomBrady
#| fig-cap: "Model Summary of Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."
#| fig-alt: "Model Summary of Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."

@@

```{r}
#| label: fig-arimaModifiedTomBrady
#| fig-cap: "Model Summary of modified Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."
#| fig-alt: "Model Summary of modified Autoregressive Integrated Moving Average Model fit to Tom Brady's Historical Performance by Game."

@@

```{r}
#| label: fig-arimaPeytonManning
#| fig-cap: "Model Summary of Autoregressive Integrated Moving Average Model fit to Peyton Manning's Historical Performance by Game."
#| fig-alt: "Model Summary of Autoregressive Integrated Moving Average Model fit to Peyton Manning's Historical Performance by Game."

@@

```{r}
#| label: fig-timeSeriesProjectionTomBrady
#| fig-cap: "Tom Brady's Historical and Projected Fantasy Points by Game."
#| fig-alt: "Tom Brady's Historical and Projected Fantasy Points by Game."

@@

```{r}
#| label: fig-timeSeriesProjectionPeytonManning
#| fig-cap: "Peyton Manning's Historical and Projected Fantasy Points by Game."
#| fig-alt: "Peyton Manning's Historical and Projected Fantasy Points by Game."

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeQB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Quarterbacks."
#| fig-alt: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Quarterbacks."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeRB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Running Backs."
#| fig-alt: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Running Backs."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeWR
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Wide Receivers."
#| fig-alt: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Wide Receivers."
#| code-fold: true

@@

```{r}
#| label: fig-individualFantasyPointsBayesianByAgeTE
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Tight Ends."
#| fig-alt: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Bayesian Generalized Additive Model, for Tight Ends."
#| code-fold: true
